---
title: "International Mortality Tables Overview"
date: "`r Sys.Date()`"
output: 
    rmarkdown::html_vignette: 
        toc: true
        toc_depth: 2
        fig_width: 7
        fig_height: 5
        number_sections: true
vignette: >
  %\VignetteIndexEntry{International Mortality Tables Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(magrittr)
library(MortalityTables)
mortalityTables.load("Austria_Census")
```


# Sources

* https://www.oecd-ilibrary.org/finance-and-investment/mortality-assumptions-and-longevity-risk_9789264222748-en
* https://avoe.at/
* https://aktuar.de/


## Various Links (to be processed):

* Australian population life tables (1881-2017): http://www.aga.gov.au/publications/life_table_2015-17/
* US Pri-2012 (US private sector retirement plans): https://www.soa.org/globalassets/assets/files/resources/experience-studies/2019/pri-2012-mort-tables-amount.xlsx
* US Retirement Plans Experience Studies:  https://www.soa.org/research/topics/pension-exp-study-list/
  * Mortality Improvement Scale MP-2019
  * Mortality Improvement Scale MP-2018
  * Mortality Improvement Scale MP-2017
  * Mortality Improvement Scale MP-2016
  * Mortality Improvement Scale MP-2015
  * Mortality Improvement Scale MP-2014
  * Mortality Improvement Scale BB
  * Pri-2012 Private Retirement Plans Mortality Tables
  * Pub-2010 Public Retirement Plans Mortality Tables
  * RP-2014 Mortality Tables (and RPH-2014 for headcount-weighted)
  * RP-2000 Mortality Tables
* US IRS Static mortality tables (prescribed for each year)
* Greece:
  * EAE 2005 A (life products)
  * EAE 2005 P (annuity products)
  * EAE 2005 K (projection scale)



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                             NTERNATIONAL                              ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->


# International / Supranational Tables

## International Civil servants Life Table

Source: https://www.sirp-isrp.org/index.php?option=com_content&view=article&id=1057:public-carrousel-actuaries&catid=247:public-home-carrousel&Itemid=992&lang=en

* ICSLT 2013
* ICSLT 2018

TODO





<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  AUSTRIA                              ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->


# Austria

## Annuities

Annuity tables in Austria are traditionally published by the [Actuarial Association of Austria (AVÖ)](https://avoe.at/rechnungsgrundlagen/).

### ÖVM 59/61 - RR 67

* Source: H. Nabl: ÖVM 59/61 - RR67 - 3%, Die Versicherungsrundschau, 22. Jahrgang, Heft 12, Dez. 1967, p.373--380.

```{r}
plotMortalityTables(RR67, mort.AT.census.1961.male)
```

### EROM/F 85 (Period table 2020), EROM/F G 1950 (Cohort table with age shift)

* EROM/F 85: gender-specific period tables, projected to year 2020 to account for mortality improvement
  * male+female, ages 0-99
* EROM/F G 1950: gender-specific cohort tables, base cohort 1950 with age-shifting to account for mortality improvement
  * male+female, ages 0-99
* Derived from population mortalities 1980/82 (improvements from population mortalities 1949/51 and 1980/82), with annuitants' selection factors applied
* First-order table without explicit security loadings
* Usage: Individual Annuity pricing and reserving
* Publisher: Aktuarvereinigung Österreichs (AVÖ), https://avoe.at/
* Target collective: Individual annuitants

* Usage with the `MortalityTables` package:
```{r EROMF85, results="hide"}
EROM85
EROF85

EROM.G1950
EROF.G1950
```
* Source: F.G. Liebmann, W. Schachermayer, M. Willomitzer: Zur Erstellung von Sterbetafeln EROM 85 und EROF 85, Mitteilungen der Aktuarvereinigung Österreichs, Heft 4, Dezember 1986, p. 1--52.
* Source: F.G. Liebmann, W. Schachermayer, M. Willomitzer: Die Generationen-Sterbetafeln EROM G 1950 und EROF G 1950, Mitteilungen der Aktuarvereinigung Österreichs, Heft 4, Dezember 1986, p. 54--94.

### AVÖ 1996-R

* gender-specific cohort tables with age-specific trend to account for mortality improvement (approximation via age-shifting given alternatively)
  * male+female, ages 0-112, individual and group variants
* Derived from population mortalities 1990/92 with annuitants' selection factors applied
  * Trend factors derived from short-term population trend 1980--95 and long-term population trend 1865--1990
* First-order table without explicit security loadings
* Usage: Individual and Group Annuity pricing and reserving; Minimum required by Austrian Financial Authority until publication of successor table AVÖ 2005R
* Publisher: Aktuarvereinigung Österreichs (AVÖ), https://avoe.at/
* Target collective: Individual and group annuitants

* Usage with the `MortalityTables` package:
```{r AVOe1996R, results="hide"}
AVOe1996R
AVOe1996R.male
AVOe1996R.male.av
AVOe1996R.male.group
AVOe1996R.female
AVOe1996R.female.av
AVOe1996R.female.group
```
* Source: S. Jörgen, F.G. Liebmann, F.W. Pagler, W. Schachermayer: Herleitung der Sterbetafel AVÖ 1996R für Rentenversicherungen, Mitteilungen der Aktuarvereinigung Österreichs, Heft 9, November 1997, p. 39--82.



### AVÖ 2005-R

* gender-specific cohort tables with age-specific trend to account for mortality improvement (approximation via age-shifting given alternatively)
  * male+female, ages 0-112, individual and group variants
  * unisex table published 2012 by mixing male+female tables
* Derived from population mortalities 2000/02 with annuitants' selection factors applied
  * Trend factors derived from mid-term population trend 1970--2000
* First-order table with explicit security loadings and second-order table without security loadings
* Usage: Individual and Group Annuity pricing and reserving; Current minimum required by Austrian Financial Authority
* Publisher: Aktuarvereinigung Österreichs (AVÖ), https://avoe.at/
* Target collective: Individual and group annuitants

* Usage with the `MortalityTables` package:
```{r AVOe2005R, results="hide"}
AVOe2005R
AVOe2005R.male
AVOe2005R.male.group
AVOe2005R.male.av
AVOe2005R.male.group.av
AVOe2005R.male.unloaded
AVOe2005R.male.nodamping
AVOe2005R.male.nodamping.group
AVOe2005R.male.nodamping.unloaded

AVOe2005R.female
AVOe2005R.female.group
AVOe2005R.female.av
AVOe2005R.female.group.av
AVOe2005R.female.unloaded
AVOe2005R.female.nodamping
AVOe2005R.female.nodamping.group
AVOe2005R.female.nodamping.unloaded

AVOe2005R.unisex
AVOe2005R.unisex.group
AVOe2005R.unisex.av
AVOe2005R.unisex.group.av
AVOe2005R.unisex.nodamping
AVOe2005R.unisex.nodamping.group
```
* Sources: 
  * R. Kainhofer, M. Predota, U. Schmock: [https://avoe.at/rententafel-avoe-2005r/](The New Austrian Annuity Valuation Table AVÖ 2005R), Mitteilungen der Aktuarvereinigung Österreichs, [Heft 13, pp.55--135](http://avoe.at/pdf/mitteilungen/H13_w3.pdf)
  * Aktuarvereinigung Österreichs: [https://avoe.at/rententafel-avoe-2005r-unisex/](Konstruktion der Unisex-Rententafel AVÖ 2005 R unisex), 2012
  * R. Kainhofer: [https://avoe.at/zur-angemessenheit-der-rententafel-avoe-2005-r/](Zur Angemessenheit der Rententafel AVÖ 2005-R), Arbeitskreis Rechnungsgrundlagen, Aktuarvereinigung Österreichs (AVÖ), 24.Oktober 2019





### Comparisons

```{r AT.Annuity.Comparison}
plotMortalityTables(RR67, EROM85, EROF85, EROM.G1950, EROF.G1950, AVOe1996R[, "Einzel"], AVOe2005R[c("m", "w"), "Einzel","loaded"],
                    aes = aes(color = table), Period = 2020, title = "Austrian Annuity Tables, Period 2020", 
                    legend.position = "right"
) + facet_grid(sex ~ .)

plotMortalityTables(RR67, EROM85, EROF85, EROM.G1950, EROF.G1950, AVOe1996R[, "Einzel"],AVOe2005R[c("m", "w"), "Einzel","loaded"],
                    aes = aes(color = year), YOB = 1965, title = "Austrian Annuity Tables, Cohort 1965", 
                    legend.position = "right"
) + facet_grid(sex ~ .)

```


## Population Mortality (Austrian Census tables)

#### Census tables

* gender-specific period tables
  * male+female, unisex only 2000/02 and 2010/12; ages 0--95, from 1930 on 0--100
* Based on the official census data:
  * 1868/71
  * 1879/82
  * 1889/92
  * 1899/1902
  * 1909/12
  * 1930/33
  * 1949/51
  * 1959/61
  * 1970/72
  * 1980/82
  * 1990/92
  * 2000/02
  * 2010/12
* Usage with the `MortalityTables` package:
```{r ÖVSt}
mort.AT.census
```
* Source: [Statistik Austria](http://statistik.at/web_de/statistiken/menschen_und_gesellschaft/bevoelkerung/sterbetafeln/index.html), http://statistik.at/wcm/idc/idcplg?IdcService=GET_NATIVE_FILE&RevisionSelectionMethod=LatestReleased&dDocName=022541


### Official population forecast (by Statistik Austria)

* Gender-specific forecast (middle scenario) of the mortalities to 2080
* Provided by Statistik Austria (no formal publication of the tables), can be used freely with attribution
* Usage with the `MortalityTables` package:
```{r AT.PopulationForecast, results="hide"}
mortalityTables.load("Austria_PopulationForecast")
mort.AT.forecast
mortalityTables.load("Austria_PopulationObserved")
```

### Markov-Chain-Monte-Carlo-fitted population forecast (by J. Hirz)

* Gender-specific forecast (middle scenario) of the mortalities by a MCMC-fit of age-specific trend factors
* Derived for the Austrian pension Table AVÖ 2018-P.
* Creator: Jonas Hirz
* Usage with the `MortalityTables` package:
```{r AT.PopulationForecastMCMC, results="hide"}
mortalityTables.load("Austria_PopulationMCMC")
mort.AT.MCMC
```

* Source: R. Kainhofer, J. Hirz, A. Schubert: AVÖ 2018-P - Rechnungsgrundlagen für die Pensionsversicherung, Dokumentation der Pensionstafel, Arbeitskreis Rechnungsgrundlagen, Aktuarvereinigung Österreichs (AVÖ), 30. August 2018. https://oefdv.avoe.at/rechnungsgrundlagen/


### Observed population mortalities 1947--2016 (by Statistik Austria)

* Gender-specific observations of the mortalities from1947
* Provided by Statistik Austria (no formal publication of the tables), can be used freely with attribution
* Usage with the `MortalityTables` package:
```{r AT.Observation, results="hide"}
mortalityTables.load("Austria_PopulationObserved")
mort.AT.observed.male
mort.AT.observed.female
mort.AT.observed.unisex

```

### Comparison

```{r AT.Census.Comparison}
plotMortalityTables(
  mort.AT.census[c("m", "w"),],
  
  aes = aes(color = table),
  legend.position = "right", legend.key.width = unit(2, "lines"),
  title = "Comparison of Austrian Census Mortalities"
) + labs(color = NULL) + facet_grid(sex ~ .)
```

```{r AT.Census.Projections}
plotMortalityTables(
  mort.AT.census[c("m", "w"),"2010/12"],
  mort.AT.forecast %>% mT.setDimInfo(table = "Official forecast"),
  mort.AT.MCMC[c("m", "w")] %>% mT.setDimInfo(table = "MCMC forecast"),

  YOB = 1980,
  aes = aes(color = table),
  legend.position = "right", legend.key.width = unit(2, "lines"),
  title = "Projected Austrian Population Mortalities, YOB 1980"
  
) + labs(color = NULL) + facet_grid(sex ~ .)
```

```{r AT.population.History}
plotMortalityTables(
  mort.AT.observed.male,
  mort.AT.observed.female,
  mort.AT.observed.unisex,
  
  YOB = 1940,
  aes = aes(color = sex),
  legend.position = "right", legend.key.width = unit(2, "lines"),
  title = "Historic Austrian Population Mortalities (yearly raw observations), YOB 1940"
)
```

## Occupational Pensions

### Ettl-Pagler

* gender-specific period tables for active and disabled persons (also transitions), as well as pensioners and widows
* second-order table, describing the transition probabilities of the Austrian social security system

```{r EttlPager, results="hide"}
pensionTables.load("Austria_EttlPagler")
EttlPagler.male
EttlPagler.female
```

* Source: Ettl W. und Pagler F.: "Rechnungsgrundlagen für die Pensionsversicherung",
Verlag: Verband der wissenschaftlichen Gesellschaften Österreichs, Wien, 1989

### AVÖ 1999-P - Rechnungsgrundlagen für die Pensionsversicherung - Pagler-Pagler

* gender-specific period tables for active and disabled persons (also transitions), as well as pensioners and widows
  * 2 Variants: "P" for pension reserves, "PK" for pension funds
  * 2 collectives: White-collar workers ("Angestellte") and mixed collective of white- and blue-collar workers
* second-order table, describing the transition probabilities of the Austrian social security system
* Publisher: Aktuarvereinigung Österreichs (AVÖ), Creator: Pagler & Pagler
* No documentation available

```{r AVOe1999P, results="hide"}
pensionTables.load("Austria_AVOe1999P")
AVOe1999P
```


### AVÖ 2008-P - Rechnungsgrundlagen für die Pensionsversicherung - Pagler-Pagler

* gender-specific period tables for active and disabled persons (also transitions), as well as pensioners and widows
  * 2 Variants: "P" for pension reserves, "PK" for pension funds
  * 2 collectives: White-collar workers ("Angestellte") and mixed collective of white- and blue-collar workers
* second-order table, describing the transition probabilities of the Austrian social security system
* Publisher: Aktuarvereinigung Österreichs (AVÖ), Creator: Pagler & Pagler
* No documentation available

```{r AVOe2008P, results="hide"}
pensionTables.load("Austria_AVOe2008P")
AVOe2008P
```


### AVÖ 2018-P - Rechnungsgrundlagen für die Pensionsversicherung

* gender-specific period tables for active and disabled persons (also transitions), as well as pensioners and widows
  * 2 Variants: "Rehageld" ("rehab money") considered as invalidity or considered as active
  * 2 collectives: White-collar workers ("Angestellte") and mixed collective of white- and blue-collar workers
* second-order table, describing real the transition probabilities of the Austrian social security system (2000/2010 -- 2016)
* Publisher: Aktuarvereinigung Österreichs (AVÖ), Creator: R. Kainhofer, J. Hirz, A. Schubert

```{r AVOe2018P, results="hide"}
pensionTables.load("Austria_AVOe2018P")
AVOe2018P
```
* Source: R. Kainhofer, J. Hirz, A. Schubert: AVÖ 2018-P - Rechnungsgrundlagen für die Pensionsversicherung, Dokumentation der Pensionstafel, Arbeitskreis Rechnungsgrundlagen, Aktuarvereinigung Österreichs (AVÖ), 30. August 2018. https://oefdv.avoe.at/rechnungsgrundlagen/

### Comparisons
```{r AT.pensionTables.Comparison}
plotMortalityTables(
  EttlPagler.male %>% pT.getSubTable("qx"),
  AVOe1999P["m",,"IP", "P"] %>% pT.getSubTable("qx"),
  AVOe2008P["m",,"IP", "P"] %>% pT.getSubTable("qx"),
  AVOe2018P["m",,"IPRG"] %>% pT.getSubTable("qx"),
  legend.position = c(0.01, 0.99), legend.justification = c(0,1),
  title = "Comparison of Austrian Pension Tables"
) + labs(color = NULL)

plotMortalityTables(
  EttlPagler.male %>% pT.getSubTable("hx"),
  AVOe1999P["m",,"IP", "P"] %>% pT.getSubTable("hx"),
  AVOe2008P["m",,"IP", "P"] %>% pT.getSubTable("hx"),
  AVOe2018P["m",,"IPRG"] %>% pT.getSubTable("hx"),
  # legend.position = c(0.01, 0.99), legend.justification = c(0,1),
  title = "Comparison of Austrian Pension Tables",
  log = FALSE, legend.position = "bottom"
) + labs(color = NULL)
```

## Experience Tables

### Gesamtbestand (total portfolio) of life insurance companies 2012--16

* gender-specific experience tables (period tables for 2012--16, central year 2014) for the whole Austrian insurance portfolio
  * separated into tradiional and unit-linlked contracts
* Experience mortality and lapse rates for the total portfolio of all Austrian Life insurance companies, 2012-2016
* Publisher: Aktuarvereinigung Österreichs (AVÖ)
* Creator: G. Friesacher, Th. Spanninger, R. Kainhofer
 Usage with the `MortalityTables` package:
```{r VUGesamtbestand, results = "hide"}
mortalityTables.load("Austria_VUGesamtbestand_2012-16")
VU.Gesamtbestand
VU.Gesamtbestand.Storno
VU.Gesamtbestand.Detail
```
```{r VUGesamtbestand.vergleich}
plotMortalityTables(VU.Gesamtbestand, legend.position = c(0.01, 0.99), legend.justification = c(0,1), title = "Austrian insurance portfolio moratlities 2012-16")
```
  
Source: G. Friesacher, Th. Spanninger, R. Kainhofer: Gesamtbestandstafel -- 
    Lebensversicherungsbestand in Österreich von 2012 bis 2016, Arbeitskreis 
    Rechnungsgrundlagen, Aktuarvereinigung Österreichs (AVÖ), 24. Oktober 2019. 
    https://avoe.at/referenzsterbetafel-und-stornovektor-des-gesamtbestands-2012-16/


### Gesamtbestand (total portfolio) of Austrian Pension Funds (Pensionskassen) 2010--16

* gender-specific experienc tables (period tables for 2010--16, central year 2013) for the four largest Austrian pension funds
  * mortalities and lapse rates
* Experience mortality and lapse rates for the total portfolio of the four largest Austrian pension funds, 2010-2016
* Publisher: Aktuarvereinigung Österreichs (AVÖ)
* Creator: R. Kainhofer
 Usage with the `MortalityTables` package:
```{r PKGesamtbestand, results = "hide"}
mortalityTables.load("Austria_PK-Bestand_2010-16")
PKBestandstafel.2010.16
```
```{r PKBestand.vergleich}
plotMortalityTables(PKBestandstafel.2010.16[,,"qx", "raw"], legend.position = "right", title = "Austrian pension fund mortalities 2010-16", aes = aes(color = type)) +
  facet_grid(sex ~ .) + labs(color = "Collective")
PKBestandstafel.2010.16[1,1,1,1]
```



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  BELGIUM                              ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Belgium

* MR/FR 
* MK/FK (required by authorities), Makeham Law of Mortality
* HFR 68-72 (census 1968-72)



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  BREAZIL                              ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->



# Brazil

## Annuities
* 1996 US Annuity 2000 Basic table
* BR-EMS 2010 (13 economic conglomerates, 82% market share)

## Pension Plans
* 1983 IAM (1983a)



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  CANADA                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->



# Canada

## Experience Tables
* CIA 1969-75
* CIA 1982-88
  * Transactions SoA 1991-92 Reports, pp.701--729

## Annuities
* GAM-94 / CIA minimum improvement base (=UP-94 with margin of 7%)

## Pension Plans
* UP-94 / Scale AA
* CPM4
* CPM2014



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  CHILE                                ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Chile

Tables in use:
* RV2009 (Annuities' experience)



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  CHINA                                ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# China

Tables in use:
* CL(2000-2003)




<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  DENMARK                                ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# DENMARK

Tables in use:
* G82 (mortality and disability); Makeham law




<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  FINLAND                              ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Finland

Tables in use:
* Statutory TyEL Mortality 2016




<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  FRANCE                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# France

Tables in use:
* TGH/TGF 2005 (French Population)
* INSEE 2014-2016 (published by French National Institute of Statistics; https://www.ined.fr/en/everything_about_population/data/france/deaths-causes-mortality/mortality-tables/)
* INSEE 2012-2014
* Historic period tables (1806-1997):
   https://www.ined.fr/Xtradocs/cdrom_vallin_mesle/contenu.htm



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  GERMANY                              ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->



# Germany

Tables in use:

* Allgemeine Deutsche Sterbetafel 1924/26 -- Endowments (until 1980s)
* Sterbetafel 1967 (modified Sterbetafel der BRD 1960/62) -- Endowments (1970s-1980s)
* Sterbetafel 1986 -- Endowments
* Sterbetafel 1986 T -- Endowments (1980s--1994)
* DAV 1994-T -- Endowments (1994--)
* Sterbetafel der BRD 1949/51 -- Annuities (until 1980s)
* Sterbetafel 1987 R -- Annuities (1980s--1994)
* DAV 1994-R -- Annuities (1994--2004)
* DAV 2004-R -- Annuities (2004--)


https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx
https://aktuar.de/unsere-themen/lebensversicherung/Seiten/sterbetafeln.aspx



## Annuities

### Sterbetafel 1987 R

* Cohort life table using age-shift to account for mortality improvements
  * Based on German population mortality 1981/83 (Trend from 1901-1983)
  * Cohort life table 1950 as base for the age-shift
* Usage with the `MortalityTables` package:
```{r Sterbetafel1987R, results = "hide"}
mortalityTables.load("Germany_Annuities_Sterbetafel1987R")
Sterbetafel1987R
Sterbetafel1987R.male
Sterbetafel1987R.female
```
  * Source: Lühr, K.-H.: Neue Sterbetafeln für die Rentenversicherung, Blätter DGVM XVII (1986), 485--513. https://link.springer.com/article/10.1007/BF02808817
  

### DAV 1994 R: 

* gender-specific tables, Base table 2000 with age-specific trends
    * male+female, ages 0-111
* approximation using age-shifting is provided (central YOB 1955)
  * Usage with the `MortalityTables` package:
```{r DAV1994R, results = "hide"}
mortalityTables.load("Germany_Annuities_DAV1994R")
DAV1994R
DAV1994R.male
DAV1994R.male.av
DAV1994R.female
DAV1994R.female.av
```
* Source: [Deutsche Aktuarvereinigung (DAV)](https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx), [https://aktuar.de/unsere-themen/lebensversicherung/sterbetafeln/UT_LV_5.pdf]
* Source: Schmithals B. und Schütz E. U. (1995): "Herleitung der DAV-Sterbetafel 1994 R für
Rentenversicherungen", Blätter der Deutschen Gesellschaft für
Versicherungsmathematik, Band XXII, Heft 1 
  
### DAV 2004 R:

  * gender-specific tables, Base table 1999 with age-specific trends
    * male+female, ages 0-121
  * First- and Second-Order Tables are provided, as well as a reserving table for existing business ("Bestand" and "B20")
  * Variants Aggregate and Select tables (5 years) are provided
  * Usage with the `MortalityTables` package: (only Aggregate tables)
```{r DAV2004R, results="hide"}
mortalityTables.load("Germany_Annuities_DAV2004R")
DAV2004R

DAV2004R.male
DAV2004R.male.selekt
DAV2004R.male.2Ord
DAV2004R.male.2Ord.selekt
DAV2004R.male.Bestand
DAV2004R.male.Bestand.selekt
DAV2004R.male.B20
DAV2004R.male.B20.selekt

DAV2004R.male.av
DAV2004R.male.Bestand.av
DAV2004R.male.B20.av  

DAV2004R.female
DAV2004R.female.selekt
DAV2004R.female.2Ord
DAV2004R.female.2Ord.selekt
DAV2004R.female.Bestand
DAV2004R.female.Bestand.selekt
DAV2004R.female.B20
DAV2004R.female.B20.selekt

DAV2004R.female.av
DAV2004R.female.Bestand.av
DAV2004R.female.B20.av  

```
  * Source: [Deutsche Aktuarvereinigung (DAV)](https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx), https://aktuar.de/unsere-themen/lebensversicherung/sterbetafeln/2018-01-24_DAV-Richtlinie_Herleitung_DAV2004R.pdf


### Comparison

```{r DE.Annuities.Comparison}
plotMortalityTables(
  Sterbetafel1987R,
  DAV1994R.male, DAV1994R.female, 
  DAV2004R.male, DAV2004R.male.2Ord, 
  DAV2004R.female, DAV2004R.female.2Ord,
  
  Period = 2000, aes = aes(linetype = sex, color = interaction(table, data)), 
  legend.position = c(0.01, 0.99), legend.justification = c(0,1), legend.key.width = unit(2, "lines"),
  title = "Comparison of German Annuity Tables, Period 2000"
) + labs(linetype = NULL, color = NULL)

plotMortalityTrend(
  DAV1994R.male, DAV1994R.female, 
  DAV2004R.male, DAV2004R.male.2Ord, 
  DAV2004R.female, DAV2004R.female.2Ord,

  Period = 2000, aes = aes(linetype = sex, color = interaction(year, data)), 
  legend.position = c(0.99, 0.99), legend.justification = c(1,1), legend.key.width = unit(2, "lines"), 
  title = "Age-specific trends of German Annuity Tables, Period 2000"
) + labs(linetype = NULL, color = NULL) + theme(legend.box.just = "right")
```


## Population Mortality (German Census tables)

* gender-specific period tables
  * male+female, unisex only 2000/02 and 2010/12; ages 0--95, from 1930 on 0--100
* Based on the official census data:
  * 1871/80
  * 1881/90
  * 1891/1900
  * 1901/10
  * 1910/11
  * 1924/26
  * 1932/34
  * 1949/51
  * 1960/62
  * 1970/72
  * 1986/88

* Usage with the `MortalityTables` package:
```{r ADSt}
mortalityTables.load("Germany_Census")
mort.DE.census
```
* Source: Allgemeine Sterbetafeln, abgekürzte Sterbetafelnund Sterbetafeln, 1871/1881 bis 2008/2010. Wiesbaden. Statist. Bundesamt. Artikel 5126202109005, Mai 2012. https://www.statistischebibliothek.de/mir/receive/DESerie_mods_00002188




### Comparison

```{r DE.Census.Comparison}
plotMortalityTables(
  mort.DE.census,
  
  aes = aes(color = table),
  legend.position = "right", legend.key.width = unit(2, "lines"),
  title = "Comparison of German Census Mortalities"
) + labs(color = NULL) + facet_grid(sex ~ .)
```


## Tables for contract with death characteristics (Life Insurances, Endowments)

### Association Table of Assured Lives 1986
[TODO]

* Base on German Population Mortality Table 1981/83

### DAV 1994 T

* gender-specific cohort table for German whole life insurances
* Based on the German Population Mortality Table 1986/88
* Generated: Deutsche Aktuarvereinigung (DAV), "Life-Insurance" committee
* Publisher: Deutsche Aktuarvereinigung (DAV), https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx

* Usage with the `MortalityTables` package:
```{r DAV1994T,results="hide"}
mortalityTables.load("Germany_Endowments_DAV1994T")
DAV1994T.male
DAV1994T.male.2Ord
DAV1994T.female
DAV1994T.female.2Ord

```
* Source: H. Loebus: Bestimmung einer angemessenen Sterbetafel für Lebensversicherungen mit Todesfallcharakter, Blätter DGVM XXI (1994), 497--524. https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx

### DAV 2008 T, DAV 2008 T R/NR


* gender-specific cohort table for German whole life insurances
* Based on reinsurance data 2001--2004 (47 German insurance companies)
* Generated: Deutsche Aktuarvereinigung (DAV), "Life-Insurance" committee
* Publisher: Deutsche Aktuarvereinigung (DAV), https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx
* Minimum standard prescribed by the DAV to be used for reserving unit-linked, endowment and whole life insurances in Germany

* Usage with the `MortalityTables` package:
```{r DAV2008T,results="hide"}
mortalityTables.load("Germany_Endowments_DAV2008T")
DAV2008T.male
DAV2008T.male.2Ord
DAV2008T.male.nonsmoker
DAV2008T.male.nonsmoker.2Ord
DAV2008T.male.smoker
DAV2008T.male.smoker.2Ord

DAV2008T.female
DAV2008T.female.2Ord
DAV2008T.female.nonsmoker
DAV2008T.female.nonsmoker.2Ord
DAV2008T.female.smoker
DAV2008T.female.smoker.2Ord
```
* Source: Herleitung der Sterbetafel DAV 2008 T für Lebensversicherungen mit Todesfallcharakter, [https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx](Deutsche Aktuarvereinigung (DAV)), 22.11.2008. https://aktuar.de/unsere-themen/lebensversicherung/sterbetafeln/2018-10-05_DAV-Richtlinie_Herleitung_DAV2008T.pdf
* Source: Raucher- und Nichtrauchersterbetafeln für Lebensversicherungen mit Todesfallcharakter, [https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx](Deutsche Aktuarvereinigung (DAV)), 22.11.2008. https://aktuar.de/unsere-themen/lebensversicherung/sterbetafeln/2018-10-05_DAV-Richtlinie_Herleitung_DAV2008T_R_NR.pdf


### Comparisons

```{r DAV-T.comparison}
plotMortalityTables(
  DAV1994T.male, DAV1994T.male.2Ord, DAV2008T.male, DAV2008T.male.2Ord, DAV2008T.male.nonsmoker,  DAV2008T.male.smoker,
  DAV1994T.female, DAV1994T.female.2Ord, DAV2008T.female, DAV2008T.female.2Ord, DAV2008T.female.nonsmoker,  DAV2008T.female.smoker,
  aes = aes(color = interaction(year, collar), linetype = data), legend.position = "right", legend.key.width = unit(1.5, "lines"),
  title = "German whole life mortality tables"
) + facet_grid(sex ~ .)
``` 


## Mortality Tables for Compulsory Private Health Insurance (PKV)

Period mortality tables for compulsory private health care insurance in Germany. The mortality tables are created annually by the PKV-Verband and published by the authorities (BaFin).

* PKV Sterbetafel 2004
* PKV Sterbetafel 2007
* PKV Sterbetafel 2008
* PKV Sterbetafel 2009
* PKV Sterbetafel 2010
* PKV Sterbetafel 2011
* PKV Sterbetafel 2012
* PKV Sterbetafel 2013
* PKV Sterbetafel 2014
* PKV Sterbetafel 2015
* PKV Sterbetafel 2016
* PKV Sterbetafel 2017
* PKV Sterbetafel 2018
* PKV Sterbetafel 2019
* PKV Sterbetafel 2020
* PKV Sterbetafel 2021

Source: BaFin, https://www.bafin.de/SharedDocs/Downloads/DE/Statistik/PKV/dl_st_2021_pkv_sterbetafel_va.html, https://www.bafin.de/SiteGlobals/Forms/Suche/Expertensuche_Formular.html?templateQueryString=PKV+Sterbetafel
Source: PKV Verband, https://www.pkv.de/service/zahlen-und-fakten/pflichtveroeffentlichungen/


```{r PKVTables}
plotMortalityTables(PKVSterbetafel, aes = aes(color = table), legend.position = "right") + facet_grid(sex~.)
```

## Occupational Disability

### DAV 1997 I
[TODO]
https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx

* Source: Kolster N., Loebus H. und Mörtlbauer W. (1998): "Neue Rechnungsgrundlagen für die
Berufsunfähigkeitsversicherung DAV 1997", Blätter der Deutschen Gesellschaft
für Versicherungsmathematik, Band XXIII, Heft 4 

### DAV 1998 EU
[TODO]
https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx

### DAV 2001 EM/EM-T
[TODO]
https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx


## MTPL Annuities

### DAV 1997 HUR

* gender-specific cohort table for German whole life insurances
  * Mortality improvement modelled using trend factors (taken from DAV 1994 R) and approximation via age-shift
* Base table Based on German TPL-annuitant data
* Generated: Deutsche Aktuarvereinigung (DAV), "HUK-Versicherungen" committee
* Publisher: Deutsche Aktuarvereinigung (DAV), https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx

* Usage with the `MortalityTables` package:
```{r DAV1997HUR,results="hide"}
mortalityTables.load("Germany_MTPL_DAV1997HUR")
DAV1997HUR
DAV1997HUR.male
DAV1997HUR.female
DAV1997HUR.av
```
* Source: Sterbetafel 1997 HUR, DAV-Mitteilungen Nr. 8, , 1997. https://aktuar.de/Dateien_extern/DAV/LV/UT_LV_10.pdf





### DAV 2006 HUR
[TODO]
https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx


## Old-Age Care
[TODO]

### DAV 2008 P
[TODO]


## Occupational Pensions

### Heubeck Richttafeln 1959
[TODO]

* Source: G. Heubeck, K. Fischer: Richttafeln für die Pensionsversicherung, René
Fischer Verlag, Weissenburg/Bayern, 1959

### Heubeck Richttafeln 1983
[TODO]

* Source: Heubeck K.: "Richttafeln", Verlag: Heubeck-Richttafeln-GmbH, Köln, 1983

### Heubeck Richttafeln 1998
[TODO]

* Source: Heubeck K.: "Richttafeln 1998", Verlag Heubeck-Richttafeln-GmbH, Köln, 1998

### Richttafeln DAV 2005-G
[TODO]

https://aktuar.de/unsere-themen/lebensversicherung/Seiten/default.aspx
* Source: Klaus Heubeck, Richard Herrmann und Gabriele D’Souza. „Die Richttafeln 2005 G – Modell, Herleitung, Formeln“. In: Blätter der DGVFM 27.3 (Apr. 2006), S. 473–517.


### Heubeck Richttafeln 2018-G
[TODO]


<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                   IRELAND                                             ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Ireland

## Population Mortality

https://www.cso.ie/en/statistics/birthsdeathsandmarriages/archive/irishlifetables1926to2012/

* gender-specific period tables
  * male+female, ages 0--105, earlier tables gave only $l_x$ and $e_x$, but no $q_x$
* Central Statistics Office life tables:
  * Irish Life Table No. 1 1925-1927
  * Irish Life Table No. 2 1935-1937
  * Irish Life Table No. 3 1940-1942
  * Irish Life Table No. 4 1945-1947
  * Irish Life Table No. 5 1950-1952
  * Irish Life Table No. 6 1960-1962
  * Irish Life Table No. 7 1965-1967
  * Irish Life Table No. 8 1970-1972
  * Irish Life Table No. 9 1978-1980
  * Irish Life Table No. 10 1980-1982
  * Irish Life Table No. 11 1985-1987
  * Irish Life Table No. 12 1990-1992
  * Irish Life Table No. 13 1995-1997
  * Irish Life Table No. 14 2001-2003
  * Irish Life Table No. 15 2005-2007
  * Irish Life Tables No. 16 2010-2012

* Usage with the `MortalityTables` package:
```{r IrishCensus}
#mortalityTables.load("Irish_Census")
#mort.IE.census
```
* Source: Central Statistics Office, https://www.cso.ie/en/statistics/birthsdeathsandmarriages/irishlifetables/



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  ISRAEL                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Israel

Tables in use:
* Israel Mortality Tables 2013



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  ITALY                                ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Italy

Tables in use:
* ISTAT2018 (Mortality table provided by the Italian National Institute of Statistics)
* ISTAT2014



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  JAPAN                                ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Japan

Tables in use:
* SMT 2007 (for Annuities; Japanese population)
* EPI tables (for Pension Plans; Census tables with experience from publich Employees' pension insurance)



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  Korea                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Korea

Tables in use:
* 6th EMT (insured lives and corporate pension schemes)
* 2018 Korea Standard Mortality (KIDI)



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  MEXICO                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Mexico

## Annuities
* EMSSAH-CMG-09
* EMSSAM-CMG-09 (minimum mortality tables)

## Pension Plans
* EMSSAH 97, EMSSAM-97



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                   NETHERLANDS                                         ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Netherlands

## Prognosetafel

* Prognosetafel 2010-2060
* Prognosetafel 2012
* Prognosetafel 2014
* Prognosetafel 2016
* Prognosetafel 2018
* Prognosetafel 2020 (https://www.ag-ai.nl/view.php?action=view&Pagina_Id=998)

https://www.ag-ai.nl/view.php?action=view&Pagina_Id=612
https://www.ag-ai.nl/view.php?action=view&Pagina_Id=888

*  Period tables: https://www.ag-ai.nl/view.php?action=view&Pagina_Id=612



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  NORWAY                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Norway

Tables in use:
* K2013



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  PERU                                 ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Peru

Tables in use:
* RV2004 modified adjusted (Chilean annuity+social security experience, modified to Peruvian experience)



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  SPAIN                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Spain

Tables in use:
* PEM/F-2000
* PERM/F 2000 (spanisch population and Swiss population)
* PERM/F 2000P



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                                  SWEDEN                               ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Sweden

Tables in use:
* DUS06
* DUS14
  * https://www.svenskforsakring.se/dus14



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                   SWITZERLAND                                          ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# Switzerland

## Pensions

### EVK -- Eidgenössische Versorgungskasse
* EVK 1950
* EVK 1960
* EVK 1970
* EVK 1980
* EVK 90
* EKV 2000
  * Kaspar Rufibach, Manuel Bertschy, Manuela Schuettel, Michael Vock, Tina Wasserfallen: Eintrittsraten und Austrittswahrscheinlichkeiten EVK 2000, Mitteilungen der Schweizerischen Aktuarvereinigung, 2001(1), 49-70
* EKV 2010

### VZ  -- Versicherungskasse der Stadt Zürich
* VZ 1950
* VZ 1960
* VZ 1970
* VZ 1980
* VZ 90
* VZ 2000
* VZ 2005
* VZ 2010
* VZ 2015
  * https://www.pkzh.ch/pkzh/de/index/publikationen/technische-grundlagen-vz.html
* VZ 2020

### BVG / LPP

* BVG 2000
* BVG 2005
* BVG 2010
  * http://www.bvg2010.ch/; Experience data of the participating institutions 2005--2009
* BVG 2015
  * http://www.bvg-grundlagen.ch/

## Annuities

* ERM/F 2000

## Population



<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                   UNITED KINGDOM                                      ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# United Kingdom

## Population

* UK, GB, England, Wales, Scotland & Northern Ireland National Life Tables  
    * Yearly observed tables from 1980-82 to 2017-19
    * https://www.ons.gov.uk/peoplepopulationandcommunity/birthsdeathsandmarriages/lifeexpectancies/bulletins/nationallifetablesunitedkingdom/2017to2019/relateddata

Usage in R:
```{r UKNationalLifeTables}
mort.UK.national

plotMortalityTables(
  mort.UK.national.UK.male,
  mort.UK.national.UK.female,
  mort.UK.national.GB.male,
  mort.UK.national.GB.female,
  mort.UK.national.EW.male,
  mort.UK.national.EW.female,
  mort.UK.national.Eng.male,
  mort.UK.national.Eng.female,
  mort.UK.national.Wales.male,
  mort.UK.national.Wales.female,
  mort.UK.national.Sco.male,
  mort.UK.national.Sco.female,
  mort.UK.national.NI.male,
  mort.UK.national.NI.female,
  Period = 2018,
  aes = aes(color = country),
  legend.position = "right",
  legend.key.width = unit(2, "line")
) + facet_grid(sex~.) + labs(color = NULL)

```

## Annuities

* PCMA/PCFA 2000 tables (UK insurance company annuitants)

## Pension Plans

* Self-Administered Pension Scheme (SAPS) tables series 1 / 2

## CMI

https://www.actuaries.org.uk/learn-and-develop/continuous-mortality-investigation/cmi-mortality-and-morbidity-tables

* A1924-29	Permanent Assurances, males, combined
* A1949-52	Permanent Assurances, males, combined
* A1967-70	Permanent Assurances, males, combined
* A1967-70(5) 	Permanent Assurances, males, combined - five years select
* a(55)m, a(55)f	Immediate Annuitants, lives
* a(90)m, a(90)f	Immediate Annuitants, lives
* FA1975-78	Permanent Assurances, males, combined
* PA(90)m, PA(90)f	Life Office Pensioners, Normals, amounts



## A1924-29

## '80' Series Tables

* AM80	Permanent Assurances, Males
* AF80 	Permanent Assurances, Females
* AM80(5)	Permanent Assurances, Male
* TM80	Temporary Assurances, Males
* PML80	Pensioners, Males, Lives
* PMA80	Pensioners, Males, Amounts
* PFL80	Pensioners, Females, Lives
* PFA80	Pensioners, Females, Amounts
* IM80	Annuitants, Males
* IF80	Annuitants, Females
* WL80	Widows, Lives
* WA80	Widows, Amounts

Source: CMI: 80 Series base mortality tables 

## '92' Series Tables

‘92’ series mortality tables for assured lives, annuitants and pensioners

* AM92	Permanent Assurances, Males
* AF92	Permanent Assurances, Females
* TM92	Temporary Assurances, Males
* TF92	Temporary Assurances, Females
* PML92	Pensioners, Males, Lives
* PMA92	Pensioners, Males, Amounts
* PMA92	Pensioners, Males, Amounts (C=2010)
* PFL92	Pensioners, Females, Lives
* PFA92	Pensioners, Females, Amounts
* PFA92	Pensioners, Females, Amounts (C=2010)
* IML92	Immediate Annuitants, Males, Lives
* IMA92	Immediate Annuitants, Males, Amounts
* IFL92	Immediate Annuitants, Females, Lives
* IFA92	Immediate Annuitants, Females, Amounts
* RMV92	Retirement Annuitants, Males, Vested
* RFV92	Retirement Annuitants, Females, Vested
* WL92	Widows, Lives
* WA92	Widows, Amounts 

Source: CMI: 92 Series base mortality tables, https://www.actuaries.org.uk/learn-and-develop/continuous-mortality-investigation/cmi-mortality-and-morbidity-tables/92-series-tables


## ‘00’ series tables

Final values of mortality rates for the "00" series assured lives mortality tables for assured lives, annuitants, and pensioners
* AMC00	Permanent Assurances, males, combined
* AMS00	Permanent Assurances, males, smokers
* AMN00	Permanent Assurances, males, non-smokers
* AFC00	Permanent Assurances, females, combined
* AFS00	Permanent Assurances, females, smokers
* AFN00	Permanent Assurances, females, non-smokers
* TMC00	Temporary Assurances, males, combined
* TMS00	Temporary Assurances, males, smokers
* TMN00	Temporary Assurances, males, non-smokers
* TFC00	Temporary Assurances, females, combined
* TFS00	Temporary Assurances, females, smokers
* TFN00	Temporary Assurances, females, non-smokers

Final values of mortality rates for the "00" series annuitant and pensioner mortality tables

* IML00	Immediate Annuitants, males, lives
* IFL00	Immediate Annuitants, females, lives
* PNML00	Pensioners, males, Normal, lives
* PNMA00	Pensioners, males, Normal, amounts
* PEML00	Pensioners, males, Early, lives
* PEMA00	Pensioners, males, Early, amounts
* PCML00	Pensioners, males, Combined, lives
* PCMA00	Pensioners, males, Combined, amounts
* PNFL00	Pensioners, females, Normal, lives
* PNFA00	Pensioners, females, Normal, amounts
* PEFL00	Pensioners, females, Early, lives
* PEFA00	Pensioners, females, Early, amounts
* PCFL00	Pensioners, females, Combined, lives
* PCFA00	Pensioners, females, Combined, amounts
* WL00	Widows, lives
* WA00	Widows, amounts
* RMD00	Retirement Annuitants, males, deferred
* RMV00	Retirement Annuitants, males, vested
* RMC00	Retirement Annuitants, males, combined
* RFD00	Retirement Annuitants, females, deferred
* RFV00	Retirement Annuitants, females, vested
* RFC00	Retirement Annuitants, females, combined
* PPMD00	Personal Pensioners, males, deferred
* PPMV00	Personal Pensioners, males, vested
* PPMC00	Personal Pensioners, males, combined
* PPFD00	Personal Pensioners, females, deferred
* PPFV00	Personal Pensioners, females, vested
* PPFC00	Personal Pensioners, females, combined


Source: CMI: 00 Series tables, https://www.actuaries.org.uk/learn-and-develop/continuous-mortality-investigation/cmi-mortality-and-morbidity-tables/00-series-tables



## ‘S1’ series tables

‘S1’ series of mortality tables for assured lives, annuitants and pensioners

* S1PFL	All pensioners (excluding dependants), Female, Lives
* S1PFA	All pensioners (excluding dependants), Female, Amounts
* S1PFA_L	All pensioners (excluding dependants), Female, Amounts, Light
* S1PFA_H	All pensioners (excluding dependants), Female, Amounts, Heavy
* S1PML	All pensioners (excluding dependants), Male, Lives
* S1PMA	All pensioners (excluding dependants), Male, Amounts
* S1PMA_L	All pensioners (excluding dependants), Male, Amounts, Light
* S1PMA_H	All pensioners (excluding dependants), Male, Amounts, Heavy
* S1DFL	Dependants, Female, Lives
* S1DFA	Dependants, Female, Amounts
* S1DFA_L	Dependants, Female, Amounts, Light
* S1DFA_H	Dependants, Female, Amounts, Heavy
* S1NFA	Normal Health pensioners, Female, Amounts
* S1NFA_L	Normal Health pensioners, Female, Amounts, Light
* S1NFA_H	Normal Health pensioners, Female, Amounts, Heavy
* S1NMA	Normal Health pensioners, Male, Amounts
* S1NMA_L	Normal Health pensioners, Male, Amounts, Light
* S1NMA_H	Normal Health pensioners, Male Amounts, Heavy
* S1IFA	Ill-health pensioners, Female, Amounts
* S1IMA	Ill-health pensioners, Male, Amounts

Source: CMI: S1 Series tables, https://www.actuaries.org.uk/learn-and-develop/continuous-mortality-investigation/cmi-mortality-and-morbidity-tables/s1-series-tables

## 'S2' Series Tables

NOT publically available!

Source: CMI: 

## Mortality Projections

https://www.actuaries.org.uk/learn-and-develop/continuous-mortality-investigation/cmi-working-papers/mortality-projections

## CMI  Morbidity Tables

Morbidity tables
“08” Series accelerated critical illness tables	Based on 2007-2010 experience collected from UK insurance companies, published in CMI Working Paper 94, 2017.
"AC04" series critical illness tables	Diagnosis rate tables based on 2003-2006 experience of accelerated critical illness policies collected from UK insurance companies, published in CMI Working Paper 50  (2010). See also CMI Working Paper 52 and CMI Working Paper 58 (both 2011).
"IP11" income protection tables	Claim inception and termination rates for individual income protection based on 2007-2016 experience of individual income protection policies collected from UK insurance companies, released alongside Working Paper 136 (2020).
“IP06” income protection tables

Claim inception rates for individual income protection based on 2003-2010 experience of individual income protection policies collected from UK insurance companies, released alongside Working Paper 120 (2019).
"IPM 1991-98" income protection tables	"Type A" inception rate tables for occupation class 1 males based on 1991-1998 experience of income protection policies collected from UK insurance companies. The development of these rates is documented in a number of papers, with an overview contained in CMI Working Paper 48. The spreadsheet contains inception rates only - termination rates can be derived by a formula.
"SM1975-78" income protection tables tables	These tables were based on 1975-1978 experience of income protection (or Permanent Health Insurance) policies collected from UK insurance companies. They are published in CMI Report 12 (1991) but are not available in a spreadsheet.

https://www.actuaries.org.uk/learn-and-develop/continuous-mortality-investigation/cmi-mortality-and-morbidity-tables

<!-- ################################################################################ -->
<!-- ################################################################################ -->
<!-- ####                   UNITED STATES OF AMERICA                            ##### -->
<!-- ################################################################################ -->
<!-- ################################################################################ -->

# United States of America

Source: [https://content.naic.org/sites/default/files/pbr_data_valuation_manual_current_edition.pdf] (Appendix M)

[TODO]

* 1941 CSI Table (Commissioners' Standard Industrial Mortality Table)
* 1941 SSI Table (Sub-Standard Industrial Mortality Table)

* 1960 CSG (Commissioners Standard Group Basic Mortality Table), Experience and Basic tables
* 1961 Standard Industrial Tables
* 1961 CSI Extended Term Tables

  

* Commissioners 1960 Standard Group Mortality Table
  * [Transactions SoA 1961, Vol.13 No.37](https://www.soa.org/globalassets/assets/library/research/transactions-of-society-of-actuaries/1961/january/tsa61v13pt1n37ab30.pdf)
  
* 1960 Commissioners' Standard Group Mortality Table
* 1961 Commissioners Standard Industial Mortality Table (1961 CSI), Proceedings of NAIC, 1961, Vol II, pp.538--540
* 1961 Commissioners Industial Extended Term Insurance Table (1961 CIET), Proc.NAIC, 1961 Vo. II. pp.541-543
* 2017 Commissioners Standard Guaranteed Issue Mortality Tables (2017 CSGI)

* 2015 Preneed Basic 
  * https://www.soa.org/resources/experience-studies/2017/preneed-mortality-report/
* UP-1984

* 1951 GAM
* 1955 American Annuity
* 1963 Annuity Experience
* 1966 Group Annuity Experience
* 1971 GAM
* 1971 IAM
* 1973 Annuity Experience
* 1983 IAM
* 1983 GAM
* 1983a
* 1994 GAM 
* 1996 IAM
* Annuity 2000
* 2012 IAM

* UP-1984 (Unisex Pension)
* UP-94
* RP-2000 (Retirement Plan)
* RP-2014 + Scale MP-2014, MP-2015, MP-2016, MP-2017, MP-2018, MP-2019, MP-2020
* RPH-2014
* PubT-2010, PubS-2010, PubG-2010, PubNS-2010, Pub-2010 + Headcount versions
* Pri-2012, Pri.H-2012


* 2000-2004 Preneed Mortality Table
* SAA Mortality Rates (Period, 1900-2007)
* IRS 2009/2010/2011/2012/2013/2014/2015/2016

* Sub-Standard Industrial Mortality Table

## Accidental Death Benefits

* 1926--33 Intercompany Double Indemnity Table for Accidental Death Benefits
* 1951-56 Accidental Death Experience
  * Transactions of the Society of Actuaries 1958
* 1959 Accidental Death Benefits Table
  * Norman Brodie and William J. November: A New Table for Accidental Death Benefits, Transactions of Society of Actuaries, 1959 Vol. 11 No. 31, pp.749--
  
Usage in R:
```{r AccidentalDeathBenefitsUS}
plotMortalityTables(
  US.AccDeath.1926, US.AccDeath.1951.56.Experience, US.AccDeath.1959,
  legend.position = c(0.01, 0.99), legend.justification = c(0,1),
  legend.key.width = unit(2, "lines"))
```

## Annuities (individual and group)

* 1971 IAM (Individual Annuity Mortality)
* 1983 GAM (Group Annuity Mortality)
* 1983 Table a IA (Individual Annuity)
* 1994 GAR (Group Annuity Reserving)
* 1996 IAM (Individual Annuity Mortality)
* 2012 IAR (Individual Annuity Reserving)
* Annuity 2000 


* 1983 Group Annuity Mortality Table without Projection
* Annuity 2000 Mortality Table
* 2012 Individual Annuity Reserve Valuation Table (2012 IAR = 2012 IAM Period Table + Scale G2
  * 2012 IAM Basic table with selection factors $F_x$ (when little or no experience is available on a business sgment (VM-21 Section 11 B.3)

* 1983 IAM (1983a)
* GAM-94 generational tables using Scale AA 
  * UP-94 table with 7% margin

## Whole Life Insurances

* 1941 CSO Table
  * Harry W. Jones, “The Commissioner’s 1941 Mortality Table” written discussion of “ The Commissioner’s 1941 Standard Mortality Table, Vol. XLII, Page 314”, Transaction of the Society of Actuaries of America, Vol. XLIII (1942) p. 85
* 1958 CSO and CET Tables
  * Industry Actuarial Advisory Committee of the Society of Actuaries. “General”, Transactions of the Society of Actuaries, Vol. X, No. 28. (1958), http://www.soa.org/library/research/transactions-of-society-of-actuaries/1958/january/tsa58v10n2827.pdf. p 42
  * Female extension: Society of Actuaries “Section II. “Female Extension of the 1958 CSO and CET Mortality Tables”, Transactions of Society of Actuaries, Vol. XI, No. 31 (1959), http://www.soa.org/library/research/transactions-of-society-of-actuaries/1959/january/tsa59v11n3193.pdf
  * ALB: Society of Actuaries, “Report of the Committee for the Preparation of Monetary Tables. I. 1958 CSO and CET Mortality Tables on the Age Last Birthday Basis.”,  Transactions of the Society of Actuaries Vol. 13, No. 37. (1961), http://www.soa.org/library/research/transactions-of-society-of-actuaries/1961/january/tsa61v13pt1n37ab31.pdf
* 1980 CSO and CET Mortality Tables (Composite, Smoker/Non-Smonker, Blended); Proc. NAIC, 180 Vol. I, p.598, 1984 pp.406--413; 1984 pp.396-400
  * Composite: 
    * “Report of the Special Committee to Recommend New Mortality Tables For Valuation”, Transactions of the Society of Actuaries, Vol. XXXIII, Society of Actuaries. (1981), http://www.soa.org/Library/Research/Transactions-Of-Society-Of-Actuaries/1981/January/tsa81v3323.pdf,
    * Committee to Recommend New Mortality Tables for Valuation, "1980 CSO and 1980 CET Mortality Tables on an Age Last Birthday Basis", Transactions Society of Actuaries Vol.  XXXIII, Society of Actuaries (1981) p. 673. http://www.soa.org/Library/Research/Transactions-Of-Society-Of-Actuaries/1981/January/tsa81v3324.pdf
  * Smoker/Nonsmoker: 
    * http://www.soa.org/library/research/transactions-reports-of-mortality-moribidity-and-experience/1980-89/1982/january/tsr8210.pdf
  * Blended:
    * Robert J. Johansen, et al., “Report of the Society of Actuaries Committee on Nonforfeiture and Valuation Mortality Problems - Individual Life Insurance and Annuities, November 28, 1983 Blended 1980 CSO and 1980 CET Mortality Tables”, Transactions of the Society of Actuaries Vol. XXXVII , Society of Actuaries (1983) Appendix E, http://www.soa.org/Library/Research/Transactions-Of-Society-Of-Actuaries/1985/January/tsa85v3712.pdf
  * Selection Factors:
    * Special Committee to Recommend new Mortality Tables for Valuation, “Report on Development of Selection Factors to be Applied to Tables K as an Alternative Method of Determining Life Insurance Reserves and Deficiency Reserve Requirements”, Transactions of the Society of Actuaries, Vol. XXXIII, Society of Actuaries (1981), http://www.soa.org/Library/Research/Transactions-Of-Society-Of-Actuaries/1981/January/tsa81v3323.pdf
* 2001 CSO (Commissioners Standard Ordinary), Mortality Table (NAIC minimum for policies 2017-2019)
  * https://www.actuary.org/content/cso-task-force-report
* 2001 CSO Preferred
  * https://www.soa.org/resources/experience-studies/2005-2009/intl-2001-cso-preferred-class-structure-mortality-tables/
* 2017 Commissioners' Standard Ordinary (CSO) Tables (NAIC minimum for policis 2020-)
  * https://www.soa.org/resources/experience-studies/2015/2017-cso-tables/


```{r CSO}
plotMortalityTables(CSO1941, CSO1941.basic, title = "1941 CSO tables")

plotMortalityTables(CSO1958, CET1958, CSO1958.basic, aes = aes(color = sex), title = "1958 CSO and CET tables") + facet_grid(table ~ageType)

plotMortalityTables(CSO1980, aes = aes(color = sex)) + facet_grid(ageType ~ collar)
plotMortalityTables(CSO1980.basic, aes = aes(color = sex)) + facet_grid(ageType ~ collar)
plotMortalityTables(CSO1980.basic, aes = aes(color = collar, linetype = sex))

# Selection effects of 1980 CSO table
plotMortalityTables(
  CSO1980[c(1,4,7),"ANB","Composite"] %>% mT.setDimInfo(SelectionAge = "Ultimate"),
  CSO1980.select[c(1,4,7),"ANB","Composite"] %>% getPeriodTable(Period = 1980, selectionAge = 20, ages = 20:99) %>% mT.setDimInfo(SelectionAge = 20),
  CSO1980.select[c(1,4,7),"ANB","Composite"] %>% getPeriodTable(Period = 1980, selectionAge = 40, ages = 40:99) %>% mT.setDimInfo(SelectionAge = 40),
  CSO1980.select[c(1,4,7),"ANB","Composite"] %>% getPeriodTable(Period = 1980, selectionAge = 60, ages = 60:99) %>% mT.setDimInfo(SelectionAge = 60),
  CSO1980.select[c(1,4,7),"ANB","Composite"] %>% getPeriodTable(Period = 1980, selectionAge = 80, ages = 80:99) %>% mT.setDimInfo(SelectionAge = 80),
 aes = aes(color = as.factor(SelectionAge)),
 legend.position = "right", title = "1980 CSO selection effects",
 legend.key.width = unit(2, "lines")
) + facet_grid(sex~.) + labs(color = "Selection age")


plotMortalityTables(CSO2001.Preferred[,,"ANB",], legend.position = "bottom", title = "CSO 2001 Preferred") + facet_grid(sex ~ collar) + aes(color = Preferred)

plotMortalityTables(CSO2017) + facet_grid(ageType ~ collar) + aes(linetype = loaded, color = sex)

plotMortalityTables(CSO2017) + facet_grid(sex ~ ageType) + aes(linetype = loaded, color = collar)
plotMortalityTables(CSO2017.Preferred[,,"ANB",,]) + facet_grid(sex ~ collar) + aes(linetype = loaded, color = Preferred)


```

## Experience Tables

"Basic Select and Ultimate" tables are raw experience data, typically without smoothing, 
while "VBT" apply smoothing on top of the basic table.

* 1925-39 Basic Tables
  * Transactions American Society of Actuaries, Vol.XLII Part 11, pp.181--187
* 1946-49 Basic Tables
  * [Transactions SoA 1950 Vol.2 No.4, pp.505--512](https://www.soa.org/globalassets/assets/library/research/transactions-of-society-of-actuaries/1950/january/tsa50v2n457.pdf)
* 1955-60 Basic Tables
  * [Transactions SoA 1962 Reports, pp.44--58](https://www.soa.org/globalassets/assets/library/research/transactions-reports-of-mortality-moribidity-and-experience/1960-69/1962/january/TSR623.pdf)
* 1965-70 Basic Select and Ultimate
  * ANB: [Transactions SoA 1973 Reports, pp.199--223](https://www.soa.org/globalassets/assets/library/research/transactions-reports-of-mortality-moribidity-and-experience/1970-79/1973/january/TSR735.pdf)
  * ALB: [Transactions SoA 1977 Vol.29](http://www.soa.org/Library/Research/Transactions-Of-Society-Of-Actuaries/1977/January/tsa77v295.pdf)
* 1975-80 Basic Select and Ultimate; 15 years select
  * [Transactions SoA 1982 Reports, pp.55--81](https://www.soa.org/globalassets/assets/library/research/transactions-reports-of-mortality-moribidity-and-experience/1980-89/1982/january/TSR823.pdf)
  * [Transactions SoA 1986 Reports, pp.205--227](https://www.soa.org/globalassets/assets/library/research/transactions-of-society-of-actuaries/1986/january/tsa86v3810.pdf)
* 1985-90 Basic Select and Ultimate, 25 years select
  * https://www.soa.org/resources/experience-studies/1990-1999/final-85-90-basic-select/
* 1990-95 Basic Select and Ultimate Tables
  * https://www.soa.org/resources/experience-studies/2000-2004/90-95-basic-select
  
* 2001 VBT (Valuation Basic Table)
  * https://www.soa.org/resources/experience-studies/2005-2009/final-report-life-insurance-valuation
* 2008 VBT (Valuation Basic Table)
  * https://www.soa.org/resources/experience-studies/2005-2009/2008-vbt-report-tables/
* 2015 VBT (Valuation Basic Table)
  * https://www.soa.org/resources/experience-studies/2015/2015-valuation-basic-tables/


```{r USABasicSelect}
plot(
  US.1925.39.Basic,
  USA.1946.49.Basic,
  USA.1955.60.Basic.U, USA.1955.60.Basic.M, USA.1955.60.Basic.F,
  
  USA.1965.70.Basic[,"ALB"],
  USA.1975.80.Basic[,"ALB"],
  USA.1985.90.Basic[,"ALB"],
  USA.1990.95.Basic[,"ALB"],
  VBT2001[,"ALB","Composite"],
  VBT2008[,"ALB","Composite"],
  VBT2015[,"ALB","Unismoke"],
  
  aes = aes(color = table),
  legend.position = "right", legend.key.width = unit(2, "lines")
) + facet_grid(sex~.)
```

```{r 1990BasicSelect.Variants}
plotMortalityTables(
  USA.1990.95.Basic.Breakdown, aes = aes(color = ageType), legend.position = "bottom", 
  title = "Breakdown-Variants of the USA 1990-95 Basic Select Table"
) +
  facet_grid(collar ~ sex)
```


```{r USA.VBT}
plotMortalityTables(
  VBT2001[,"ALB",],
  
  aes = aes(color = table, linetype = collar),
  legend.position = "right", legend.key.width = unit(2, "lines")
) + facet_grid(sex~.)
```
## Pension Plans

### RP-2000
Projected beyond 2000 using scale AA

### RP-2014 / MP-2014

Source: Society of Actuaries. RP-2014 Mortality Tables Report. Techn. Ber. Okt. 2014. URL: https://www.soa.
org/experience-studies/2014/research-2014-rp/.
Source: Society of Actuaries. Mortality Improvement Scale MP-2014 Report. Techn. Ber. Okt. 2014. URL: https:
//www.soa.org/experience-studies/2014/research-2014-mp/.


